% // ..................what is mongodb...............................//

MongoDB is a NoSQL, document-oriented database designed for high performance, scalability,
and flexibility. Unlike traditional relational databases that use tables and rows, 
MongoDB stores data in flexible, JSON-like documents.


% .......................Key Concepts of MongoDB.............................///

> Document :

The basic unit of data in MongoDB, similar to a row in a relational database.
Stored in BSON (Binary JSON) format.

eg:

{
  "_id": 1,
  "name": "John Doe",
  "age": 29,
  "address": {
    "street": "123 Main St",
    "city": "New York"
  }
}

>  Collection:

A group of documents, similar to a table in relational databases.
Collections do not enforce a schema, so documents in a collection can have different fields.
Example: users collection can store different user documents.

>  Database:

A physical container for collections. Each database gets its own set of files on the file system.
You can have multiple databases in MongoDB.

>  _id Field:

A unique identifier for each document. If not provided, MongoDB automatically generates one.
Similar to a primary key in relational databases.

> BSON (Binary JSON):

MongoDB stores data in BSON format, which is a binary representation of JSON-like documents.

% .................................Basic MongoDB Commands.................................. //

% Connect to MongoDB:

mongo
% /..........................{Create or Switch to a Database}.....

use myDatabase


% Insert a Document:

db.users.insertOne({
  "name": "John Doe",
  "age": 29,
  "email": "john@example.com"
})
% .........................Find Documents:

% Retrieve all documents from a collection:


db.users.find()

% Retrieve documents with specific criteria:

db.users.find({ age: 29 })

% ...........Update a Document:

db.users.updateOne(
  { name: "John Doe" },
  { $set: { age: 30 } }
)
% .........Delete a Document:

db.users.deleteOne({ name: "John Doe" })

% ..........................Create an Index:

% Indexes help MongoDB to search data faster.

db.users.createIndex({ name: 1 })

% ........Show Databases: 
show dbs

% ........Show Collections:

show collections
% ....... Drop a Collection:

db.users.drop()
%....... Drop a Database:

db.dropDatabase()

%  ................................Use Cases for MongoDB:.....................................

Content Management Systems: MongoDB’s flexibility allows storing different types of content.
Real-time Analytics: The database can handle large volumes of real-time data.
Internet of Things (IoT): MongoDB’s ability to scale and store varied data structures makes it ideal for IoT applications.
E-commerce Applications: It is often used to manage product catalogs and user data.
MongoDB is highly flexible and a popular choice for developers working on modern, data-driven applications.

// const db=mongoose.